Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update todo
Figure ref 7
Fix intro to section 8.1

We can assume that Stockholm, being one of the more developed cities in one of the most technologically connected country in the world, would be fairly well mapped in OSM. The positional accuracy has improved by roughly 3.5 meters since the study by (Haklay, 2010), and by roughly 1.5 meters since the study by (Fan et al, 2014), if the SLU reference dataset is to be believed as absolute.

The completeness analysis by building area shows that the OSM Stockholm dataset has high completeness in terms of both building area and counted features, in the same level as the study of Munich by (Fan et al, 2014).

The difference in area cover can partially be explained by small utility buildings that are often not represented in the OSM dataset.
Particularily the residential areas in downtown, Stockholm, are characteristic in that each city block consists of a street front and an open, communal compound in the middle, inside of which there are usually a number of small utility buildings such as bicycle garages, toolsheds, refuse rooms and such.
These buildings are likely hard to make out and trace on publicly available satellite image data.
They are, according to (Fan et al, 2014) occluded by their surroundings due to shadows or forestry.
This appears to be a large consensus in the field.

@@

% TODO: Interview with Todor
% TODO: Figure showing how turning function is calculated from edges and angles

>>>>

One could reasonably assume that Stockholm, being one of the more developed cities in one of the most technologically connected country in the world, would be fairly well mapped in OSM.
Let us take the positional accuracy of the Stockholm area, as obtained by this study, as reprentative of that of major cities in developed countries in the OSM dataset.
Then the positional accuracy has improved by roughly 3.5 meters since the study by (Haklay, 2010), and by roughly 1.5 meters since the study by (Fan et al, 2014).
This of course assumes that the SLU reference dataset is taken as absolute.

The completeness analysis by building area shows that the OSM Stockholm dataset has high completeness in terms of both building area and counted features, in the same level as the study of Munich by (Fan et al, 2014).
The difference in area cover can partially be explained by small utility buildings that are often not represented in the OSM dataset.
Particularily the residential areas in downtown, Stockholm, are characteristic in that each city block consists of a street front and an open, communal compound in the middle, inside of which there are usually a number of small utility buildings such as bicycle garages, toolsheds, refuse rooms and such.
See figure \ref{fig:osm-slu-map-utility-buildings} for an example of an area in stockholm with such characteristics.
These buildings are likely hard to make out and trace on publicly available satellite image data.
They are, according to (Fan et al, 2014) occluded by their surroundings due to shadows or forestry.
This appears to be a large consensus in the field.

@@

% TODO: Reformat 8.3 to show the suggested algorithms in a list, with figure references
% TODO: Complementary text in the results section
% TODO: Proper citations (Fix links)

% TODO: Figure showing how turning function is calculated from edges and angles
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Expand on analysis about Feature overlap

% After response from Todor:
% TODO: Write section: Utility in real world applications
% TODO: Spell check
% TODO: Go over report one final time
